Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-05 envolve.tex
ref the right equ

\begin{numcases}{}
\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
\label{equ:latent1}\\
\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
\end{numcases}
This model \eqref{equ:latent1} - \eqref{equ:elo4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet. \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector. This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.

>>>>

\begin{numcases}{}
\min_{p_*,q_*,b_*}\sum_{(u,i)\in\kappa}\left(r_{ui} -\mu - b_u - b_i - p^T_uq_i \right)^2 + \lambda_3 \left( \|p_u\|^2 + \|q_i\|^2 + b_u^2 + b_i^2 \right)
\label{equ:latent1}\\
\hat{r}_{ui} = b_{ui} + p^T_uq_i \label{equ:latent2}\\
b_{ui} = \mu + b_u + b_i \label{equ:latent3} \\
\kappa =\{(u,i)|r_{ui}\text{is known}\} \label{equ:latent4}
\end{numcases}
This model \eqref{equ:latent1} - \eqref{equ:latent4}, $b_u$ and $b_i$ indicate the observed deviations of user $u$ and item $i$, respectively from the average, $\mu$ is the overall rating average, set $\kappa$ represent all the translations has been made yet. \eqref{equ:latent2} use the technique called Singular Value Decomposition that evaluate a matrix of preference value by the product of each one's parameters vector. This model can be solved by Gradient Descent method and $p_*,q_*,b_*$ are the optimal value.
